---
output: github_document
editor_options:
  markdown:
    mode: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  # fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# spirit: Shiny App to the [sprtt](https://meikesteinhilber.github.io/sprtt/ "https://meikesteinhilber.github.io/sprtt/") Package on CRAN

<!-- badges: start -->

[![codecov](https://codecov.io/gh/MeikeSteinhilber/sprtt/branch/master/graph/badge.svg?token=IQHTDTRBAW)](https://codecov.io/gh/MeikeSteinhilber/sprtt) [![R-CMD-check-ubuntu20.04](https://github.com/MeikeSteinhilber/spirit/actions/workflows/R-CMD-check-ubuntu20.4.yaml/badge.svg?branch=master)](https://github.com/MeikeSteinhilber/spirit/actions/workflows/R-CMD-check-ubuntu20.4.yaml) [![R-CMD-check-windows-macOs](https://github.com/MeikeSteinhilber/spirit/actions/workflows/R-CMD-check-windows-macOs.yaml/badge.svg?branch=master)](https://github.com/MeikeSteinhilber/spirit/actions/workflows/R-CMD-check-windows-macOs.yaml) [![lint](https://github.com/MeikeSteinhilber/spirit/actions/workflows/lint.yaml/badge.svg?branch=master)](https://github.com/MeikeSteinhilber/spirit/actions/workflows/lint.yaml)

<!-- badges: end -->

## Open the app

Please click [**here**](https://meike-steinhilber.shinyapps.io/spirit/ "https://meike-steinhilber.shinyapps.io/spirit/") to open the app in your internet browser!

## Requirements to use the app

-   **Internet connection** (otherwise you have to install the app locally on your computer)

-   No R knowledge is required to use the app

-   No installation of R & RStudio is necessary

The `spirit` app allows you to use the [sprtt](https://meikesteinhilber.github.io/sprtt/ "https://meikesteinhilber.github.io/sprtt/") package via a user interface. The [sprtt](https://meikesteinhilber.github.io/sprtt/ "https://meikesteinhilber.github.io/sprtt/") package is the implementation of **s**equential **p**robability **r**atio **t**ests using the associated **t**-statistic (**sprtt**).

## Installation

There is no need to install the `spirit` shiny app on your computer - you can access the app on the internet! Please click [**here**](https://meike-steinhilber.shinyapps.io/spirit/ "https://meike-steinhilber.shinyapps.io/spirit/") to open the app in your browser!

If you want to use the app *without* an internet connection, please download the app as an R package on your computer. To run the app locally on your computer, R (and RStudio) have to be already installed .

### Development version from GitHub

To get a bug fix or to use a feature from the development version, you can install the development version from GitHub.

```{r, eval=FALSE}
# the installation requires the "devtools" package
# install.packages("devtools")
devtools::install_github("MeikeSteinhilber/spirit")
```
