---
output: github_document
editor_options:
  markdown:
    mode: gfm
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  # fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# sprtt Shiny App

<!-- badges: start -->

[![test-coverage](https://github.com/MeikeSteinhilber/Snowflake/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/MeikeSteinhilber/Snowflake/actions/workflows/test-coverage.yaml) 

<!-- badges: end -->

## Overview

Snowflake is the shiny app to the sprtt package on CRAN.

The `sprtt` package is the implementation of **s**equential **p**robability **r**atio **t**ests using the associated **t**-statistic (**sprtt**).

The package contains:

-   `seq_ttest()` calculates the sequential test statistic and

-   three data sets (`df_income`, `df_stress`, `df_cancer`) to run the examples in the documentation

## Installation

### Development version from GitHub

To get a bug fix or to use a feature from the development version, you can install the development version from GitHub.

```{r, eval=FALSE}
# the installation requires the "devtools" package
# install.packages("devtools")
devtools::install_github("MeikeSteinhilber/Snowflake")
```


